\documentclass{article}

\usepackage{amsmath}
\usepackage{comment}
\usepackage[letterpaper]{geometry}
\usepackage{hyperref}
\usepackage{parskip}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=black,
}
\urlstyle{tt}

\urlstyle{same}

\geometry{margin=0.875in}

\pagenumbering{gobble}

\renewcommand{\baselinestretch}{1.25}

\begin{document}
  % ------------------------------------------------------------
  %   Header
  % ------------------------------------------------------------
  \hrule height 1pt
  \begin{center}
    {\Large \textbf{Corey Redmon}}\\
    redmoncoreyl@gmail.com -- (803) 372-7871
  \end{center}
  \vspace{0.1in}
  \hrule height 1pt

  \setlength{\parskip}{0.0in}
  \setlength{\parindent}{0.4in}

  % ------------------------------------------------------------
  %   Work Experience
  % ------------------------------------------------------------
  \paragraph{Work Experience} $ $

  \hangindent=0.8in
  Senior Software Engineer -- Persistent Systems (formerly SCI Fusion360) \hfill October 2021 -- Present \newline
  -- Managed strong relationships with three banking clients and one marketing client. \newline
  -- Delivered documentation of several payment processing systems for Frost Bank. \newline
  -- Developed an automated deployment process for Frost Bank. \newline
  -- Developed system for processing mortgage payment files for Frost Bank.

  \hangindent=0.8in
  Associate Software Developer -- SCI Fusion360 \hfill January 2019 -- October 2021 \newline
  -- Aided with product support for IBM's Financial Transaction Manager. \newline
  -- Provided support by finding solutions to defects in IBM's Financial Transaction Manager. \newline
  -- Developed automated unit tests for BB\&T's Zelle Client Care Tool. \newline
  -- Developed new features for BB\&T's Zelle Client Care Tool. \newline
  -- Provided iOS Swift development support for Retail Sports Marketing.

  \hangindent=0.8in
  Teaching Assistant -- Clemson University School of Computing \hfill August 2017 -- December 2018 \newline
  -- Taught computer science labs for Algorithms and Data Structures. \newline
  -- Graded computer science projects, papers, and exams. \newline
  -- Held office hours to answer students' questions about the course.

  % ------------------------------------------------------------
  %   Development Portfolio
  % ------------------------------------------------------------
  \paragraph{Development Portfolio} \hfill (see \href{http://github.com/redmoncoreyl}{\texttt{http://github.com/redmoncoreyl}})%

  \hangindent=0.5in
  \textit{PageRank Search Engine} --- Implements Google's Page Rank algorithm
  for web search using random walks and a subnetwork of the internet in order to
  rank pages matching a given search.

  \hangindent=0.5in
	\textit{Turing Machine Interpreter} --- Uses formal definition of Turing machine to
  interpret input files which specify a Turing machine and compute output. Also includes
  example Turing machine files.

  \hangindent=0.5in
	\textit{C-lite Interpreter} --- Develops a new programming language, C-lite, which
  is a simplified version of C. Also includes an interpreter for this language and
  example C-lite programs.

  % ------------------------------------------------------------
  %   Areas of Focus
  % ------------------------------------------------------------
  \paragraph{Skills, Abilities, and Certifications} $ $

  \hangindent=0.4in
  -- Professional Scrum Master I issued by Scrum.org \newline
  -- Proficient in Java, C++, JavaScript, HTML, CSS, SQL, Python. \newline
  -- Knowledgeable with source version control systems, defect tracking, and documentation. \newline
  -- Training in and experience with Agile methodology. \newline
  -- Strong communication skills and ability to work in teams. \newline
  -- Committed to continuous learning and professional development.

  % ------------------------------------------------------------
  %   Education
  % ------------------------------------------------------------
  \paragraph{Education} $ $

  \hangindent=0.8in
  Master of Science, Computer Science \hfill December 2018 \newline
  Clemson University \newline

  \hangindent=0.8in
  Bachelor of Science, Computer Science \hfill May 2017 \newline
  Clemson University
  
\end{document}
